### 2021-10-26 paper/pldi22/formal.tex
Transformations in formalization

We first define $\ires$ as a specification language to describe JavaScript
semantics.  Then, we introduce a general formalization of function
specialization in $\ires$. Finally, we define a constant propagation
specialization as its an instance to reduce JavaScript semantics using given
syntactic views. We also prove its semantics preservation.

@@

\[
  \begin{array}{lr@{~}c@{~}c@{~}c@{~}l}
    \text{Functions} & \funcset &\ni& \func &::=&
    \kwdef \; \varx \; \kwrl \varx^* \kwrr \; \lab\\

@@

@@

    \text{Instructions} & \instset &\ni& \inst &::=&
    \refer = \expr \mid
    \varx = \expr \kwrl \expr^* \kwrr \mid
    \kwif \; \expr \; \lab \; \lab \mid
    \kwret \; \expr\\

    \text{Expressions} & \exprset &\ni& \expr &::=&
    \pval \mid
    \op \kwrl \expr^* \kwrr \mid
    \kwcl \kwcr \mid
    \refer\\

@@

An $\ires$ program $\prog = (\istset, \getinst, \getnext)$ consists of initial
states and two mappings; $\getinst: \labset \rightarrow \instset$ maps labels to
their instructions, and $\getnext: \labset \rightarrow \labset$ maps labels to
their next labels, where a label $\lab \in \labset$ denotes a program point.  A
function $\func \in \funcset$ is defined with its name, parameters, and body
label.  For presentation brevity, we assume that no global variables exist in
this paper.  An instruction $\inst \in \instset$ is an assignment $\refer =
\expr$, a function call $x = \expr \kwrl \expr^* \kwrr$, a branch $\kwif \;
\expr \; \lab \; \lab$, or a return instruction $\kwret \; \expr$.  An
invocation of an abstract algorithm in ECMAScript is compiled to a function call
instruction with a new temporary variable.  We represent loops using branch
instructions with cyclic pointing of labels in $\getnext$.  An expression is a
primitive value $\pval$, an operation $\op \kwrl \expr^* \kwrr$, an object
allocation $\kwcl \kwcr$, or a reference $\refer$.  A reference is a variable
$x$ or an object field $\expr \kwsl \expr \kwsr$.  We write $\expr.\varf$ to
briefly represent $\expr \kwsl \code{"f"} \kwsr$.

@@

\paragraph{Expressions} We define the denotational semantics of expressions with
the following form:
\[
  \framebox{$\sem{\expr}: \stset \rightarrow \stset \times \valset$}
\]
For each expression $\expr \in \exprset$, its semantics $\sem{\expr}$ takes a
state and returns a pair of an updated state and a value as the result of
expression. We define five different cases in the semantics of expressions as
follows:
\begin{itemize}
  \item \underline{Primitive Values}:
    \[
      \sem{\pval}(\st) =
      (\st, \pval)
    \]

  \item \underline{Operations}:
    \[
      \sem{\op \kwrl \expr_1, \cdots, \expr_n \kwrr}(\st) =
      (\st_n, \op(\val_1, \cdots, \val_n))
    \]
    where $\st_0 = \st \wedge \forall 1 \leq k \leq n. \;
    \sem{\expr_k}(\st_{k-1}) = (\st_k, \val_k)$

  \item \underline{Object Allocations}:
    \[
      \sem{\kwcl \kwcr}(\st) =
      ((\lab, \ctxts, \heap[\addr \mapsto \varnothing], \env), \addr)
    \]
    where $\st = (\lab, \ctxts, \heap, \env) \wedge \addr \not\in
    \text{Domain}(\heap)$

  \item \underline{Variable Lookups}:
    \[
      \sem{\varx}(\st) =
      (\st, \env(\varx))
    \]
    where $\st = (\_, \_, \_, \env)$

  \item \underline{Field Lookups}:
    \[
      \sem{\expr_0 \kwsl \expr_1 \kwsr}(\st) =
      (\st'', \obj(\str))
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}ll}
        \sem{\expr_0}(\st) &=& (\st', \addr) &\wedge\\
        \sem{\expr_1}(\st') &=& (\st'', \str) &\wedge\\
        \st'' &=& (\_, \_, \heap, \_) &\wedge\\
        \obj &=& \heap(\addr)\\
      \end{array}
    \]
\end{itemize}

\paragraph{Instructions} We define the denotational semantics of instructions
with the following form:
\[
  \framebox{$\sem{\inst}: \stset \rightarrow \stset$}
\]
For each instruction $\inst \in \instset$, its semantics $\sem{\inst}$ takes a
state and returns an updated state. We define five different cases in the
semantics of instructions as follows:

@@

  \item \underline{Function Calls}:
    \[
      \sem{\varx = \expr \kwrl \expr_1 \cdots \expr_n \kwrr}(\st) =
      (\lab_\varf, \ctxt :: \ctxts, \heap, \env')
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}ll}
        \sem{\expr}(\st) &=& (\st_0, \kwdef \; \varf \; \kwrl \varp_1, \cdots,
        \varp_n \kwrr \; \lab_\varf) &\wedge\\
        \sem{\expr_k}(\st_{k-1}) &=& (\st_k, \val_k) \; \forall 1 \leq k \leq n
        &\wedge\\
        \st_n &=& (\lab, \ctxts, \heap, \env) &\wedge\\
        \env' &=& [\varp_1 \mapsto \val_1, \cdots, \varp_n \mapsto \val_n]
        &\wedge\\
        \ctxt &=& (\getnext(\lab), \env, \varx)\\
      \end{array}
    \]

@@

\paragraph{Functions} Moreover, we define the denotational semantics of
functions with the following form:
\[
  \framebox{$\sem{\func}: \heapset \times \valset^* \rightarrow \heapset \times
  \valset$}
\]
For each function $\func \in \funcset$, its semantics $\sem{\func}$ takes a heap
and values as arguments, and it returns a pair of an updated heap and a return
value as follows:
\[
  \sem{\kwdef \; \varf \; \kwrl \varp_1, \cdots, \varp_n \kwrr \lab_\varf}
  (\heap, (\val_1, \cdots, \val_n)) = (\heap'', \val'')
\]
where
\[
  \begin{array}{l@{~}c@{~}ll}
    \st &=& (\lab_\varf, \epsilon, \heap, \env) &\wedge\\
    \env &=& [\varp_1 \mapsto \val_1, \cdots, \varp_n \mapsto \val_n] &\wedge\\
    \st \trans^* \st' &=& (\lab', \epsilon, \heap', \_) &\wedge\\
    \getinst(\lab') &=& \kwret \; \expr' &\wedge\\
    \sem{\expr'}(\st') &=& (\st'', \val'') &\wedge\\
    \st'' &=& (\_, \epsilon, \heap'', \_)\\
  \end{array}
\]

\subsection{Function Specialization}

A \textit{function specialization} is defined with the following three
components:
\begin{itemize}
  \item Restriction $\restrictset$
  \item Concretization $\gamma: \restrictset \rightarrow \powerset{\stset
    \times \valset^*}$
  \item Transformation $\transform: \restrictset \rightarrow \funcset
    \rightarrow \funcset$.
\end{itemize}
We can restrict possible input states and arguments of functions by defining a
set of restrictions $\restrictset$ with their concretization $\gamma:
\restrictset \rightarrow \powerset{\stset \times \valset^*}$. A transformation
$\transform: \restrictset \rightarrow \funcset \rightarrow \funcset$ is
parameteric with such restrictions and transforms a function to another function
by preserving semantics under a given restriction.

\subsubsection{Constant Propagation Specialization}
We define a \textit{constant propagation specialization} with the following
three components:

\begin{itemize}
  \item Restriction $\cprestrictset = \avalset^*$
  \item Concretization $\cpgamma: \avalset^* \rightarrow \powerset{\stset
    \times \valset^*}$ s.t.
    \[
      \cpgamma(\aval_1, \cdots, \aval_n) =
      \stset \times (\valgamma(\aval_1) \times \cdots \times \valgamma(\aval_n))
    \]
  \item Transformation $\cptransform: \avalset^* \rightarrow \funcset
    \rightarrow \funcset$
\end{itemize}
The constant propagation specialization restricts specific arguments with
concrete values with a restriction defined with a sequence of static or dynamic
values $\valset \uplus \{ \top \}$, but it does not restrict input states.
While a dynamic value $\top$ denotes no restriction, it restricts a specific
argument with the static value $\val \in \valset$. To specialize functions under
a given restriction $(\aval_1, \cdots, \aval_n) \in \avalset^*$, we
define a transformation $\cptransform: \avalset^* \rightarrow \funcset
\rightarrow \funcset$. To propagate constants, \todo What is a constant?
a constant is a value which is statically fixed under a given restriction.

\[
  \begin{array}{lr@{~}c@{~}l@{~}c@{~}l}
    \text{Abstract Environments} & \aenv &\in& \aenvset &=&
    \varset \rightarrow \avalset\\
    \text{Abstract Values} & \aval &\in& \avalset &=&
    (\valset \times \exprset) \uplus \{ \bot, \top \}\\
  \end{array}
\]

\todo $\envgamma, \valgamma, \join, \meet, \order$

\paragraph{Expressions}
\[
  \framebox{$\asem{\expr}: \aenvset \rightarrow \avalset$}
\]
\begin{itemize}
  \item \underline{Primive Values}:
    \[
      \asem{\pval}(\aenv) = (\pval, \pval)
    \]
  \item \underline{Operations}:
    \[
      \asem{\op \kwrl \expr_1, \cdots, \expr_n \kwrr}(\aenv) =
      (\aval, \expr)
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}ll}
        \asem{\expr_k}(\aenv) &=& \aval_k \; \forall 1 \leq k \leq n
        &\wedge\\
        \aval &=& \left\{
          \begin{array}{ll}
            \bot & \text{if} \; \exists k. \; \aval_k = \bot\\
            \top & \text{if} \; \exists k. \; \aval_k = \top\\
            (\val, \expr') &
            \text{if} \; \forall k. \; \aval_k = (\val_k, \expr'_k)\\
          \end{array}
        \right. &\wedge\\
        \val &=& \op(\val_1, \cdots, \val_n) &\wedge\\
        \expr' &=& \op(\expr'_1, \cdots, \expr'_n)\\
      \end{array}
    \]
  \item \underline{Object Allocations}:
    \[
      \asem{\kwcl \kwcr}(\aenv) = \top
    \]
  \item \underline{Variable Lookups}:
    \[
      \asem{\varx}(\aenv) = \aenv(\varx)
    \]
  \item \underline{Field Lookups}:
    \[
      \asem{\expr_0 \kwsl \expr_1 \kwsr}(\aenv) = \top
    \]
\end{itemize}
\[
  \framebox{$\cptransforme: \exprset \times \aenvset \rightarrow \exprset \times
  \avalset$}
\]
\[
  \cptransforme(\expr, \aenv) = (\expr'', \aval)
\]
where
\[
  \begin{array}{l@{~}c@{~}ll}
    \aval &=& \asem{\expr}(\aenv) &\wedge\\
    \expr'' &=& \left\{
      \begin{array}{ll}
        \pval & \text{if} \; \aval = (\pval, \_)\\
        \expr' & \text{if} \; \aval = (\_, \expr')\\
        \expr & \text{otherwise}\\
      \end{array}
    \right.\\
  \end{array}
\]

\paragraph{Instructions}
\[
  \framebox{$\cptransformi: \instset \times \aenvset \rightarrow \instset \times
  \aenvset$}
\]
\begin{itemize}
  \item \underline{Variable Assignments}:
    \[
      \cptransformi(\varx = \expr, \aenv) =
      (\varx = \expr', \aenv[\varx \mapsto \aval])
    \]
    where
    \[
      (\expr', \aval) = \cptransforme(\expr, \aenv)
    \]

  \item \underline{Field Assignments}:
    \[
      \cptransformi(\expr_0 \kwsl \expr_1 \kwsr = \expr_2, \aenv) =
      (\expr'_0 \kwsl \expr'_1 \kwsr = \expr'_2, \aenv)
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}ll}
        (\expr'_0, \_) = \cptransforme(\expr_0, \aenv) &\wedge\\
        (\expr'_1, \_) = \cptransforme(\expr_1, \aenv) &\wedge\\
        (\expr'_2, \_) = \cptransforme(\expr_2, \aenv)\\
      \end{array}
    \]

  \item \underline{Function Calls}:
    \[
      \cptransformi(\varx = \expr \kwrl \expr_1 \cdots \expr_n \kwrr, \aenv) =
      (\varx = \expr' \kwrl \expr'_1 \cdots \expr'_n \kwrr,
      \aenv[\varx \mapsto \top])
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}ll}
        (\expr', \_) = \cptransforme(\expr, \aenv) &\wedge\\
        (\expr'_k, \_) = \cptransforme(\expr_k, \aenv) \; \forall 1 \leq k \leq
        n\\
      \end{array}
    \]

  \item \underline{Branches}:
    \[
      \cptransformi(\kwif \; \expr \; \lab_\vart \; \lab_\varf, \aenv) =
      (\kwif \; \expr' \; \lab_\vart \; \lab_\varf, \aenv)
    \]
    where
    \[
      (\expr', \_) = \cptransforme(\expr, \aenv)
    \]

  \item \underline{Returns}:
    \[
      \cptransformi(\kwret \; \expr, \aenv) =
      (\kwret \; \expr, \aenv)
    \]
    where
    \[
      (\expr', \_) = \cptransforme(\expr', \aenv)
    \]
\end{itemize}

\paragraph{Functions}
\[
  \framebox{$\cptransform: (\avalset)^* \rightarrow \funcset \rightarrow
  \funcset$}
\]

@@

% \subsubsection{Redundancy Elimination Transformation}
% 
% \[
%   \begin{array}{lr@{~}c@{~}l}
%     \text{Restrictions} &\{ \top \}\\
%     \text{Concretization} & \gamma(\top) &=& \stset \times \valset^*\\
%   \end{array}
% \]
% 
% The redundancy elimination transformation is defined without any restriction,
% which means its restriction set consists of a single element $\top$
% representing all possible cases.  Therefore, we omit the restriction part in
% this transformation for the brevity.
% 
% \[
%   \framebox{$\transformref: \funcset \rightarrow \funcset$}
% \]
% 
% \todo

>>>>

We first define $\ires$ as a specification language to describe JavaScript
semantics.  Then, we introduce a partial evaluation in $\ires$ to reduce
JavaScript semantics using given syntactic views. We also prove its semantics
preservation.

@@

\[
  \begin{array}{lr@{~}c@{~}c@{~}c@{~}l}
    \text{Programs} & \progset &\ni& \prog &=& (\istset, \getinst, \getnext)\\

    \text{Functions} & \funcset &\ni& \func &::=&
    \kwdef \; \kwrl \varx^* \kwrr \; \lab\\

@@

    \text{Instructions} & \instset &\ni& \inst &::=&
    \refer = \expr \mid
    \varx = \kwcl \kwcr \mid
    \varx = \expr \kwrl \expr^* \kwrr \mid \\&&&&&
    \kwif \; \expr \; \lab \; \lab \mid
    \kwret \; \expr\\

@@

    \text{Expressions} & \exprset &\ni& \expr &::=&
    \pval \mid
    \op \kwrl \expr^* \kwrr \mid
    \refer\\

@@

An $\ires$ program $\prog = (\istset, \getinst, \getnext)$ consists of initial
states and two mappings; $\getinst: \labset \rightarrow \instset$ maps labels to
their instructions, and $\getnext: \labset \rightarrow \labset$ maps labels to
their next labels, where a label $\lab \in \labset$ denotes a program point.  A
function $\func \in \funcset$ is defined with its parameters and body label.
For presentation brevity, we assume that no global or captured variables exist
in this paper.  An instruction $\inst \in \instset$ is an assignment $\refer =
\expr$, an object allocation $\varx = \kwcl \kwcr$,  a function call $\varx =
\expr \kwrl \expr^* \kwrr$, a branch $\kwif \; \expr \; \lab \; \lab$, or a
return instruction $\kwret \; \expr$.  An invocation of an abstract algorithm in
ECMAScript is compiled to a function call instruction with a new temporary
variable.  We represent loops using branch instructions with cyclic pointing of
labels in $\getnext$.  An expression is a primitive value $\pval$, an operation
$\op \kwrl \expr^* \kwrr$, or a reference $\refer$.  A reference is a variable
$\varx$ or an object field $\expr \kwsl \expr \kwsr$.  We write $\expr.\varf$ to
briefly represent $\expr \kwsl \code{"f"} \kwsr$.

@@

\paragraph{Expressions} We define the denotational semantics of expressions with
the following form:
\[
  \framebox{$\sem{\expr}: \stset \rightarrow \valset$}
\]
For each expression $\expr \in \exprset$, its semantics $\sem{\expr}$ takes a
state and returns a value as the result of expression. We define four different
cases in the semantics of expressions as
follows:
\begin{itemize}
  \item \underline{Primitive Values}:
    \[
      \sem{\pval}(\st) = \pval
    \]

  \item \underline{Operations}:
    \[
      \sem{\op \kwrl \expr_1, \cdots, \expr_n \kwrr}(\st) =
      \op(\val_1, \cdots, \val_n)
    \]
    where $\forall 1 \leq k \leq n. \; \sem{\expr_k}(\st) = \val_k$

  \item \underline{Variable Lookups}:
    \[
      \sem{\varx}(\st) = \env(\varx)
    \]
    where $\st = (\_, \_, \_, \env)$

  \item \underline{Field Lookups}:
    \[
      \sem{\expr_0 \kwsl \expr_1 \kwsr}(\st) = \val
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}ll}
        \val_0 &=& \sem{\expr_0}(\st) &\wedge\\
        \val_1 &=& \sem{\expr_1}(\st) &\wedge\\
        \st &=& (\_, \_, \heap, \_) &\wedge\\
        \val &=& \left\{
          \begin{array}{ll}
            \heap(\addr)(\str)
            & \text{if} \; \val_0 = \addr \wedge \val_1 = \str\\
            \tree[k]
            & \text{if} \; \val_0 = \tree \wedge \val_1 = k\\
          \end{array}
        \right.\\
      \end{array}
    \]
\end{itemize}

\paragraph{Instructions} We define the denotational semantics of instructions
with the following form:
\[
  \framebox{$\sem{\inst}: \stset \rightarrow \stset$}
\]
For each instruction $\inst \in \instset$, its semantics $\sem{\inst}$ takes a
state and returns an updated state. We define six different cases in the
semantics of instructions as follows:

@@

  \item \underline{Object Allocations}:
    \[
      \sem{\varx = \kwcl \kwcr}(\st) =
      (\lab, \ctxts, \heap[\addr \mapsto \epsilon], \env[\varx \mapsto
      \addr])
    \]
    where $\st = (\lab, \ctxts, \heap, \env) \wedge \addr \not\in
    \text{Domain}(\heap)$ and $\epsilon$ denotes an empty object.

  \item \underline{Function Calls}:
    \[
      \sem{\varx = \expr \kwrl \expr_1 \cdots \expr_n \kwrr}(\st) =
      (\lab_\varf, \ctxt :: \ctxts, \heap, \env')
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}ll}
        \sem{\expr}(\st) &=& (\st_0, \kwdef \; \kwrl \varp_1, \cdots, \varp_n
        \kwrr \; \lab_\varf) &\wedge\\
        \sem{\expr_k}(\st_{k-1}) &=& (\st_k, \val_k) \; \forall 1 \leq k \leq n
        &\wedge\\
        \st_n &=& (\lab, \ctxts, \heap, \env) &\wedge\\
        \env' &=& [\varp_1 \mapsto \val_1, \cdots, \varp_n \mapsto \val_n]
        &\wedge\\
        \ctxt &=& (\getnext(\lab), \env, \varx)\\
      \end{array}
    \]

@@

% \paragraph{Functions} Moreover, we define the denotational semantics of
% functions with the following form:
% \[
%   \framebox{$\sem{\func}: \heapset \times \valset^n \rightarrow \heapset \times
%   \valset$}
% \]
% For each function $\func \in \funcset$, its semantics $\sem{\func}$ takes a heap
% and values as arguments, and it returns a pair of an updated heap and a return
% value as follows:
% \[
%   \sem{\kwdef \; \kwrl \varp_1, \cdots, \varp_n \kwrr \; \lab_\varf}
%   (\heap, (\val_1, \cdots, \val_n)) = (\heap'', \val'')
% \]
% where
% \[
%   \begin{array}{l@{~}c@{~}ll}
%     \env &=& [\varp_1 \mapsto \val_1, \cdots, \varp_n \mapsto \val_n] &\wedge\\
%     \st &=& (\lab_\varf, \epsilon, \heap, \env) &\wedge\\
%     \st \trans^* \st' &=& (\lab', \epsilon, \heap', \_) &\wedge\\
%     \getinst(\lab') &=& \kwret \; \expr' &\wedge\\
%     \sem{\expr'}(\st') &=& (\st'', \val'') &\wedge\\
%     \st'' &=& (\_, \epsilon, \heap'', \_)\\
%   \end{array}
% \]

\subsection{Partial Evaluation}

We define a \textit{partial evaluation} in $\ires$ as a transformation
$\transform: \funcset \times \avalset^n \rightarrow \progset$.  It takes a
target function and abstract values $\avalset^n$ to restrict specific function
parameters with static values, then it returns the transformed $\ires$ program
in the given restriction.  We first define abstract domains of states,
environments, and values as follows:
\begin{itemize}
  \item \underline{Abstract States}: $\aelemset = \labset \rightarrow \aenvset$
    \[
      \begin{array}{lcl}
        \multicolumn{3}{l}{\elemgamma: \aelemset \rightarrow \powerset{\stset}}\\
        \elemgamma(\aelem) &=& \{ \st \in \stset \mid \st = (\lab, \_, \_, \_)
        \wedge \st \in \envgamma(\aelem(\lab)) \}\\

        \aelem \order \aelem' &\Leftrightarrow& \forall \lab \in \labset. \;
        \aelem(\lab) \order \aelem'(\lab)\\

        \aelem \join \aelem' &=& \lambda \lab \in \labset. \; \aelem(\varx) \join
        \aelem(\lab)\\
      \end{array}
    \]
  \item \underline{Abstract Environments}: $\aenvset = \varset \rightarrow
    \avalset$
    \[
      \begin{array}{lcl}
        \multicolumn{3}{l}{\envgamma: \aenvset \rightarrow \powerset{\stset}}\\
        \envgamma(\aenv) &=& \{ \st \in \stset \mid \forall \varx \in \varset.
          \; (\aenv(\varx) = \langle \val, \expr \rangle) \Rightarrow\\ &&
          \phantom{\{ \st \in \stset \mid} (\sem{\varx}(\st) = \sem{\expr}(\st) =
          \val) \}\\

        \aenv \order \env' &\Leftrightarrow& \forall \varx \in \varset. \;
        \aenv(\varx) \order \aenv'(\varx)\\

        \aenv \join \aenv' &=& \lambda \varx \in \varset. \; \aenv(\varx) \join
        \aenv(\varx)\\
      \end{array}
    \]
  \item \underline{Abstract Values}: $\avalset = (\valset \times \exprset)
    \uplus \{ \top \}$
    \[
      \begin{array}{lcl}
        \multicolumn{3}{l}{\valgamma: \avalset \rightarrow \powerset{\valset}}\\
        \valgamma(\aval) &=& \left\{
          \begin{array}{ll}
            \{ \val \} & \aval = (\val, \expr) \\
            \valset & \aval = \top\\
          \end{array}
        \right.\\

        \aval \order \aval' &\Leftrightarrow&
        \aval' = \top \vee \aval = \aval'\\

        \aval \join \aval' &=& \left\{
          \begin{array}{ll}
            \aval & \text{if} \; \aval = \aval'\\
            \top & \text{otherwise}\\
          \end{array}
        \right.\\
      \end{array}
    \]
\end{itemize}
An abstract state $\aelem \in \aelemset$ is a mapping from labels to abstract
environments to represent the shape of states in each label. An abstract
environment $\aenv \in \aenvset$ is a mapping from variables to abstract values
to describe values stored in variables.  An abstract value $\aval \in \avalset$
is a static value $\langle \val, \expr \rangle$ or a dynamic value $\top$.
Since non-primitive values (e.g., addresses or JavaScript ASTs) cannot be
directly represented as expressions, each static values $\langle \val, \expr
\rangle$ also keeps another way to represent itself as an expression. Now, we
define transformations of expressions and instructions, and introduce an
iterative algorithm to proceed the partial evaluation in $\ires$.

\subsubsection{Expressions} Before defining a transformation of expressions, we
first define abstract evaluation of expressions as follows:
\[
  \framebox{$\asem{\expr}: \aenvset \rightarrow \avalset$}
\]
\begin{itemize}
  \item \underline{Primive Values}:
    \[
      \asem{\pval}(\aenv) = \langle \pval, \pval \rangle
    \]
  \item \underline{Operations}:
    \[
      \asem{\op \kwrl \expr_1, \cdots, \expr_n \kwrr}(\aenv) = \aval
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}l@{~}l}
        \asem{\expr_k}(\aenv) &=& \aval_k \; \forall 1 \leq k \leq n
        &\wedge\\
        \aval &=& \left\{
          \begin{array}{ll}
            \top & \text{if} \; \exists k. \; \aval_k = \top\\
            \langle \val, \expr' \rangle & \text{if} \; \forall k. \; \aval_k =
            \langle \val_k, \expr'_k \rangle\\
          \end{array}
        \right. &\wedge\\
        \val &=& \op(\val_1, \cdots, \val_n) &\wedge\\
        \expr' &=& \op(\expr'_1, \cdots, \expr'_n)\\
      \end{array}
    \]
  \item \underline{Variable Lookups}:
    \[
      \asem{\varx}(\aenv) = \aenv(\varx)
    \]
  \item \underline{Field Lookups}:
    \[
      \asem{\expr_0 \kwsl \expr_1 \kwsr}(\aenv) = \aval
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}l@{~}l}
        \asem{\expr_0}(\aenv) &=& \aval_0 &\wedge\\
        \asem{\expr_1}(\aenv) &=& \aval_1 &\wedge\\
        \aval &=& \left\{
          \begin{array}{ll}
            \langle \tree[k], \expr'_0 \kwsl \expr'_1 \kwsr \rangle & \text{if}
            \; \aval_0 = \langle \tree, \expr'_0 \rangle \wedge \aval_1 =
            \langle k, \expr'_1 \rangle\\
            \top & \text{otherwise}\\
          \end{array}
        \right.\\
      \end{array}
    \]
\end{itemize}
Then, we define the transformation of expressions as follows:
\[
  \framebox{$\transforme: \exprset \times \aenvset \rightarrow \exprset \times
  \avalset$}
\]
\[
  \transforme(\expr, \aenv) = (\expr'', \aval)
\]
where
\[
  \begin{array}{l@{~}c@{~}ll}
    \aval &=& \asem{\expr}(\aenv) &\wedge\\
    \expr'' &=& \left\{
      \begin{array}{ll}
        \pval & \text{if} \; \aval = \langle \pval, \_ \rangle\\
        \expr' & \text{if} \; \aval = \langle \_, \expr' \rangle\\
        \expr & \text{otherwise}\\
      \end{array}
    \right.\\
  \end{array}
\]

\subsubsection{Instructions} Now, we define a transformation of instructions
using the transformation of expressions as follows:
\[
  \framebox{$\transformi: \instset \times \aenvset \rightarrow \instset \times
  \aenvset$}
\]
\begin{itemize}
  \item \underline{Variable Assignments}:
    \[
      \transformi(\varx = \expr, \aenv) =
      (\varx = \expr', \aenv[\varx \mapsto \aval])
    \]
    where
    \[
      (\expr', \aval) = \transforme(\expr, \aenv)
    \]

  \item \underline{Field Assignments}:
    \[
      \transformi(\expr_0 \kwsl \expr_1 \kwsr = \expr_2, \aenv) =
      (\expr'_0 \kwsl \expr'_1 \kwsr = \expr'_2, \aenv)
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}ll}
        (\expr'_0, \_) = \transforme(\expr_0, \aenv) &\wedge\\
        (\expr'_1, \_) = \transforme(\expr_1, \aenv) &\wedge\\
        (\expr'_2, \_) = \transforme(\expr_2, \aenv)\\
      \end{array}
    \]
  \item \underline{Object Allocations}:
    \[
      \transformi(\varx = \kwcl \kwcr, \aenv) =
      (\varx = \kwcl \kwcr, \aenv[\varx \mapsto \top])
    \]

  \item \underline{Function Calls}:
    \[
      \transformi(\varx = \expr \kwrl \expr_1 \cdots \expr_n \kwrr, \aenv) =
      (\varx = \expr' \kwrl \expr'_1 \cdots \expr'_n \kwrr,
      \aenv[\varx \mapsto \top])
    \]
    where
    \[
      \begin{array}{l@{~}c@{~}ll}
        (\expr', \_) = \transforme(\expr, \aenv) &\wedge\\
        (\expr'_k, \_) = \transforme(\expr_k, \aenv) \; \forall 1 \leq k \leq
        n\\
      \end{array}
    \]

  \item \underline{Branches}:
    \[
      \transformi(\kwif \; \expr \; \lab_\vart \; \lab_\varf, \aenv) =
      (\kwif \; \expr' \; \lab_\vart \; \lab_\varf, \aenv)
    \]
    where
    \[
      (\expr', \_) = \transforme(\expr, \aenv)
    \]

  \item \underline{Returns}:
    \[
      \transformi(\kwret \; \expr, \aenv) =
      (\kwret \; \expr, \aenv)
    \]
    where
    \[
      (\expr', \_) = \transforme(\expr', \aenv)
    \]
\end{itemize}

\subsubsection{Fixpoint of Abstract Transfer Function}

@@
